\documentclass[a4paper,man,natbib,floatsintext,12pt]{apa7}

\usepackage[english]{babel} %character and hyphenation rules specific to the language you choose
%\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{tabularx} %great for APA-style Tables
\usepackage{siunitx} % Required for good table alignmen
\sisetup{
  round-mode          = places, % Rounds numbers
  round-precision     = 2, % to 2 places
}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{booktabs} % For nice table rules
\usetikzlibrary{shapes,decorations,arrows,calc,arrows.meta,fit,positioning}
\tikzset{
    -Latex,auto,node distance =1 cm and 1 cm,semithick,
    latent/.style ={ellipse, draw, minimum width = 0.7 cm},
    observed/.style ={rectangle, draw},
    bidirected/.style={Latex-Latex,dashed},
    el/.style = {inner sep=2pt, align=left, sloped}
}
\newcommand{\sigFtest}[4]{\textit{F}(#1,#2) = #3, \textit{p}$<$#4}
\newcommand{\nonsigFtest}[3]{\textit{F}(#1,#2) = #3, \textit{p}$>$.05}


\title{Adolescent, parent, and provider attitudes toward a machine learning based clinical decision support system for selecting treatment for youth depression}
\shorttitle{CDSS-YD Attitudes}
\authorsnames[1,2,1,3,4,{3,5},5,5]{Meredith Gunlicks-Stoessel, Yangchenchen Liu, Catherine Parkhill, Nicole Morrell, Mimi Choy-Brown, Christopher Mehus, Joel Hetler, Gerald August}
\authorsaffiliations{{Department of Psychiatry \& Behavioral Sciences, University of Minnesota, 2025 E River Parkway, 55414 Minneapolis, MN, USA},{Department of Psychology, University of Minnesota, Minneapolis, MN, USA},{Center for Applied Research and Educational Improvement, University of Minnesota, St. Paul, MN, USA},{School of Social Work, University of Minnesota, St. Paul, MN, USA},{Department of Family Social Science, University of Minnesota, St. Paul, MN, USA}}
\journal{The Best Psychology Journal EVER!}
\abstract{Background: Machine learning based clinical decision support systems (CDSSs) have been proposed as a means
of advancing personalized treatment planning for disorders, such as depression, that have a multifaceted etiology,
course, and symptom profile. However, machine learning based models for treatment selection are rare in the field of
psychiatry. They have also not yet been translated for use in clinical practice. Understanding key stakeholder attitudes
toward machine learning based CDSSs is critical for developing plans for their implementation that promote uptake
by both providers and families.
Methods: In Study 1, a prototype machine learning based Clinical Decision Support System for Youth Depression
(CDSS-YD) was demonstrated to focus groups of adolescents with a diagnosis of depression (n=9), parents (n=11),
and behavioral health providers (n=8). Qualitative analysis was used to assess their attitudes towards the CDSS-YD.
In Study 2, behavioral health providers were trained in the use of the CDSS-YD and they utilized the CDSS-YD in a
clinical encounter with 6 adolescents and their parents as part of their treatment planning discussion. Following the
appointment, providers, parents, and adolescents completed a survey about their attitudes regarding the use of the
CDSS-YD. 
Results: All stakeholder groups viewed the CDSS-YD as an easy to understand and useful tool for making
personalized treatment decisions, and families and providers were able to successfully use the CDSS-YD in clinical
encounters. Parents and adolescents viewed their providers as having a critical role in the use the CDSS-YD, and
this had implications for the perceived trustworthiness of the CDSS-YD. Providers reported that clinic productivity
metrics would be the primary barrier to CDSS-YD implementation, with the creation of protected time for training,
preparation, and use as a key facilitator.
Conclusions: Machine learning based CDSSs, if proven effective, have the potential to be widely accepted tools for
personalized treatment planning. Successful implementation will require addressing the system-level barrier of having
sufficient time and energy to integrate it into practice.}
\keywords{Clinical decision support systems, Depression, Adolescents, Health care providers, Attitudes}
\authornote{We have no known conflict of interest to disclose. Correspondence concerns this article should be addressed to Meredith Gunlicks-Stoessel
mgunlick@umn.edu}
\leftheader{Alternate page header in man mode}

%-------------- END PREAMBLE  -------------------


\begin{document}

\maketitle  %Insert my APA style title page

\input{intro.tex}

\input{method.tex}

\input{results.tex}

\input{discussion.tex}


\bibliography{reference_CDSS-YD.bib}

\end{document}
https://www.overleaf.com/project/68bc9b6676c27897cbfba1ae